brados: declarative, programmable object storage

### 2016-05-25 paper.tex
update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\lstset{frame=tb,
  language=Ruby,
  captionpos=b,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  %columns=flexible,
  basicstyle={\scriptsize\ttfamily},
  numbers=none,
  %numberstyle=\tiny\color{gray},
  %keywordstyle=\color{blue},
  %commentstyle=\color{dkgreen},
  %stringstyle=\color{mauve},
  %breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

@@

\begin{lstlisting}[caption={Trim}, label=lst:trim]
bloom :trim do
  log <+- trim_op{|op| [op.pos, 'trimmed']}
  ret <=  trim_op{|op| [op.type, op.pos, op.epoch, 'ok']}
end
\end{lstlisting}

@@

\begin{lstlisting}[caption={Write}, label=lst:write]
bloom :write do
  temp :valid_write <= write_op.notin(found_op)
  log <+ valid_write { |o| [o.pos, 'valid', o.data] }
  ret <= valid_write { |o| [o.type, o.pos, o.epoch, 'ok'] }
  ret <= write_op.notin(valid_write) { |o|
    [o.type, o.pos, o.epoch, 'read-only']
  }
end
\end{lstlisting}

@@

\subsection{Optimizer}

@@

The subset of the Bloom language we are using is powerful enough to express the
CORFU language, as well as many of the object class interfaces that are already
included in Ceph. We briefly sketch the Bloom imlementation of an object class
that provides a locking service. This is an interesting example because Bloom
implementations use mechanisms for introducing points of coordination in
execution, which in the context of Ceph, may be written in Bloom itself.

\begin{lstlisting}[caption={Hello}, label=lab]
bloom :take_lock do
end

bloom :break_lock do
end

bloom :list_locks do
end

bloom :lock_info do
end
\end{lstlisting}

>>>>

\lstset{frame=tb,
  language=Ruby,
  basicstyle={\scriptsize\sffamily},
  breaklines=true,
  captionpos=b
}

%  aboveskip=3mm,
%  belowskip=3mm,
%  showstringspaces=false,
%  %columns=flexible,
%  basicstyle={\scriptsize\ttfamily},
%  numbers=none,
%  %numberstyle=\tiny\color{gray},
%  %keywordstyle=\color{blue},
%  %commentstyle=\color{dkgreen},
%  %stringstyle=\color{mauve},
%  %breaklines=true,
%  breakatwhitespace=true,
%  tabsize=3
%}

@@

\begin{lstlisting}[caption={Trim}, label=lst:trim]
bloom :trim do
  log <+- trim_op{|o| [o.pos, 'trimmed']}
  ret <=  trim_op{|o| [o.type, o.pos, o.epoch, 'ok']}
end
\end{lstlisting}

@@

\begin{lstlisting}[caption={Write}, label=lst:write]
bloom :write do
  temp :valid_write <= write_op.notin(found_op)
  log <+ valid_write{|o| [o.pos, 'valid', o.data]}
  ret <= valid_write{|o| [o.type, o.pos, o.epoch, 'ok']}
  ret <= write_op.notin(valid_write) { |o|
    [o.type, o.pos, o.epoch, 'read-only']
  }
end
\end{lstlisting}

@@

\subsection{Optimization}

Choosing implementation details
  - the refcount example is good. small data kept in ceph object bytestream
until it becomes large then use omap.

  - could use the dataflow graph to do interesting things like understand how
  to do prefecting of things like keys or data that are often only known at
  execution time

@@

As we have seen the subset of Bloom used in Brados is powerful enough to
express the semantics of the CORFU storage interface. We briefly sketch the
implementation of an additional interface found in Ceph and used by the
S3-compatible RADOS-Gateway service.

Channel
C++ code comparison

The subset of the Bloom language we are using in Brados is powerful enough to
express the CORFU language, as well as many of the object class interfaces that
are already included in Ceph. We briefly sketch the Bloom imlementation of an
object class that provides a locking service. This is an interesting example
because Bloom implementations use mechanisms for introducing points of
coordination in execution, which in the context of Ceph, may be written in
Bloom itself.

\begin{lstlisting}[caption={Hello}, label=lab]
class RefCount
  include Bud

  state do
    table :refs, [:tag]
    channel :remove_chn
    interface input, :get_op, [:tag]
    interface input, :put_op, [:tag]
    interface output, :ret, [:status]
  end

  bloom :get do
    refs <= get_op
    ret  <= get_op{|op| ['ok']}
  end

  bloom :put do
    temp :found <= (put_op * refs).matches
    refs <- found
    ret <= put_op{|op| ['ok']}

    temp :remove <= found.notin(refs)	
    remove_chn <~ remove
  end
end
\end{lstlisting}
